Enhancement of SDR in Thessaloniki

### 2024-04-13 high_aod/GHI_enh_04_investigate.tex
Commit 2024-04-13 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-09}

@@

\begin{verbatim}
Run previous step: ./GHI_enh_03_process.R
\end{verbatim}

Attaching package: 'timetk'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:data.table':

    :=
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

Call:
stats::lm(formula = .formula, data = df)

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14

aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
inpatern
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
torun
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
2024-04-09 13:15:00.5 athan@tyler GHI_enh_03_process.R 22.842565 mins
\end{verbatim}

@@

lmD: 1.566006 +/- 0.108321

lmY: 1.566022 +/- 0.108322

Arima: 1.566405 +/- 0.146687

@@

lmD: 0.950804 +/- 0.155249

lmY: 0.950827 +/- 0.155251

Arima: 1.022268 +/- 0.236917

@@

lmD: 1.086985 +/- 0.167871

lmY: 1.087013 +/- 0.167874

Arima: 1.159971 +/- 0.251086

@@

\begin{verbatim}
Warning in sqrt(diag(se)): NaNs produced

Warning in sqrt(diag(se)): NaNs produced
\end{verbatim}

@@

lmD: 1.034078 +/- 0.239285

lmY: 1.034088 +/- 0.23929

Arima: 1.03413 +/- 0.363491

@@

lmD: 0.944568 +/- 0.252832

lmY: 0.944578 +/- 0.252837

Arima: 0.944623 +/- 0.387039

@@

lmD: 1.109672 +/- 0.07725

lmY: 1.109686 +/- 0.077252

Arima: 1.109689 +/- 0.115906

@@

lmD: 1.167512 +/- 0.073583

lmY: 1.167525 +/- 0.073584

Arima: 1.167532 +/- 0.106265

@@

lmD: 33.66024 +/- 5.69273

lmY: 33.6608 +/- 5.692829

Arima: 33.721354 +/- 8.881459

@@

lmD: 0.003266 +/- 0.000271

lmY: 0.003266 +/- 0.000271

Arima: 0.003291 +/- 0.000364

@@

lmD: 0.001715 +/- 0.000278

lmY: 0.001715 +/- 0.000278

Arima: 0.001886 +/- 0.000465

@@

lmD: 0.001677 +/- 0.000314

lmY: 0.001677 +/- 0.000314

Arima: 0.001849 +/- 0.000512

@@

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced

Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced
\end{verbatim}

@@

lmD: 0.00184 +/- 0.000301

lmY: 0.00184 +/- 0.000301

Arima: 0.00184 +/- 0.000473

@@

lmD: 0.001768 +/- 0.000292

lmY: 0.001768 +/- 0.000292

Arima: 0.001768 +/- 0.000451

@@

lmD: 0.002432 +/- 0.000235

lmY: 0.002432 +/- 0.000235

Arima: 0.002432 +/- 0.000369

@@

lmD: 0.002624 +/- 0.000229

lmY: 0.002624 +/- 0.000229

Arima: 0.002624 +/- 0.000346

@@

lmD: 0.977006 +/- 0.143935

lmY: 0.977029 +/- 0.143937

Arima: 1.040956 +/- 0.218636

@@

lmD: 0.817503 +/- 0.103432

lmY: 0.817514 +/- 0.103434

Arima: 0.817505 +/- 0.120041

@@

lmD: 0.216071 +/- 0.038072

lmY: 0.216075 +/- 0.038073

Arima: 0.216075 +/- 0.041418

@@

lmD: 0.190931 +/- 0.037875

lmY: 0.190936 +/- 0.037876

Arima: 0.190936 +/- 0.040087

@@

lmD: 0.485676 +/- 0.046388

lmY: 0.485682 +/- 0.046389

Arima: 0.485682 +/- 0.055179

@@

lmD: -0.00734 +/- 0.019077

lmY: -0.007339 +/- 0.019077

Arima: -0.007339 +/- 0.019267

@@

lmD: -0.027816 +/- 0.017696

lmY: -0.027816 +/- 0.017696

Arima: -0.027816 +/- 0.017858

@@

lmD: 0.49203 +/- 0.073274

lmY: 0.492037 +/- 0.073275

Arima: 0.492032 +/- 0.081403

@@

lmD: 0.595557 +/- 0.083417

lmY: 0.595566 +/- 0.083419

Arima: 0.59556 +/- 0.094857

@@

lmD: 1.467857 +/- 0.152656

lmY: 1.46788 +/- 0.152659

Arima: 1.467877 +/- 0.18431

@@

lmD: 0.001336 +/- 0.000137

lmY: 0.001336 +/- 0.000137

Arima: 0.001336 +/- 0.000157

@@

lmD: 0.000423 +/- 5.9e-05

lmY: 0.000423 +/- 5.9e-05

Arima: 0.000423 +/- 6.7e-05

@@

lmD: 0.000372 +/- 6.1e-05

lmY: 0.000372 +/- 6.1e-05

Arima: 0.000372 +/- 6.8e-05

@@

lmD: 2.1e-05 +/- 3.2e-05

lmY: 2.1e-05 +/- 3.2e-05

Arima: 2.1e-05 +/- 3.6e-05

@@

lmD: -1.2e-05 +/- 2.9e-05

lmY: -1.2e-05 +/- 2.9e-05

Arima: -1.2e-05 +/- 3.4e-05

@@

lmD: 0.000922 +/- 0.000106

lmY: 0.000922 +/- 0.000106

Arima: 0.000922 +/- 0.00012

@@

lmD: 0.001074 +/- 0.000117

lmY: 0.001074 +/- 0.000117

Arima: 0.001074 +/- 0.000134

@@

lmD: 0.036561 +/- 0.003622

lmY: 0.036562 +/- 0.003622

Arima: 0.036562 +/- 0.004204

@@

lmD: 0.187208 +/- 0.249476

lmY: 0.187246 +/- 0.24948

Arima: 0.171775 +/- 0.364628

@@

lmD: 0.049774 +/- 0.192505

lmY: 0.049798 +/- 0.192508

Arima: 0.008548 +/- 0.346363

@@

lmD: 0.091248 +/- 0.191453

lmY: 0.091272 +/- 0.191456

Arima: 0.049975 +/- 0.33542

@@

lmD: -0.069532 +/- 0.179279

lmY: -0.06952 +/- 0.179282

Arima: -0.124647 +/- 0.339466

@@

lmD: -0.089703 +/- 0.178956

lmY: -0.089692 +/- 0.178959

Arima: -0.144328 +/- 0.338161

@@

lmD: 0.16704 +/- 0.22968

lmY: 0.167077 +/- 0.229683

Arima: 0.146398 +/- 0.353614

@@

lmD: 0.17703 +/- 0.238162

lmY: 0.177067 +/- 0.238165

Arima: 0.158966 +/- 0.358093

@@

lmD: 0.368357 +/- 0.253498

lmY: 0.368383 +/- 0.253502

Arima: 0.36844 +/- 0.258271

@@

lmD: 0.000508 +/- 0.000281

lmY: 0.000509 +/- 0.000281

Arima: 0.000508 +/- 0.000318

@@

lmD: 0.000356 +/- 0.000214

lmY: 0.000356 +/- 0.000214

Arima: 0.000349 +/- 0.000265

@@

lmD: 0.000399 +/- 0.000221

lmY: 0.000399 +/- 0.000221

Arima: 0.000392 +/- 0.00027

@@

lmD: 0.000168 +/- 0.000199

lmY: 0.000168 +/- 0.000199

Arima: 0.000157 +/- 0.000257

@@

lmD: 0.000155 +/- 0.000199

lmY: 0.000155 +/- 0.000199

Arima: 0.000144 +/- 0.000256

@@

lmD: 0.000509 +/- 0.000261

lmY: 0.000509 +/- 0.000261

Arima: 0.000508 +/- 3e-04

@@

lmD: 0.00051 +/- 0.00027

lmY: 0.00051 +/- 0.00027

Arima: 0.000509 +/- 0.000307

@@

lmD: 0.008776 +/- 0.005507

lmY: 0.008777 +/- 0.005507

Arima: 0.008799 +/- 0.005722

@@

Arima: 0.216075 +/- 0.041418

@@

\begin{verbatim}
Warning: Removed 25 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

lmY: 341.6364 +/- 36.57038

@@

lmY: 122.2229 +/- 11.42113

@@

lmY: 0.232986 +/- 0.055703

@@

lmY: 0.183685 +/- 0.040872

@@

\begin{verbatim}
2024-04-09 13:17:00.8 athan@tyler GHI_enh_03_process.R 1.962400 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-13}

@@

@@

lmD: 1.517841 +/- 0.099133

lmY: 1.517857 +/- 0.099134

Arima: 1.518153 +/- 0.131133

@@

lmD: 0.986143 +/- 0.155127

lmY: 0.986168 +/- 0.155129

Arima: 1.050369 +/- 0.236468

@@

lmD: 1.152913 +/- 0.165733

lmY: 1.152941 +/- 0.165736

Arima: 1.217146 +/- 0.245786

@@

\begin{verbatim}
Warning in sqrt(diag(se)): NaNs produced
Warning in sqrt(diag(se)): NaNs produced
\end{verbatim}

@@

lmD: 1.06442 +/- 0.24189

lmY: 1.06443 +/- 0.241895

Arima: 1.064477 +/- 0.369173

@@

lmD: 0.965697 +/- 0.257186

lmY: 0.965706 +/- 0.25719

Arima: 0.965757 +/- 0.397302

@@

lmD: 1.086689 +/- 0.074568

lmY: 1.086704 +/- 0.07457

Arima: 1.086709 +/- 0.111711

@@

lmD: 1.121477 +/- 0.069651

lmY: 1.121491 +/- 0.069652

Arima: 1.1215 +/- 0.100263

@@

lmD: 34.75674 +/- 5.785425

lmY: 34.75733 +/- 5.785525

Arima: 34.809263 +/- 9.232706

@@

lmD: 0.00359 +/- 0.000275

lmY: 0.00359 +/- 0.000275

Arima: 0.003611 +/- 0.000363

@@

lmD: 0.001821 +/- 0.000281

lmY: 0.001821 +/- 0.000281

Arima: 0.001976 +/- 0.000461

@@

lmD: 0.001769 +/- 0.000314

lmY: 0.00177 +/- 0.000314

Arima: 0.001923 +/- 0.000501

@@

\begin{verbatim}
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
possible convergence problem: optim gave code = 1
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced
Warning in arima(x = dataset[[avar]], order = c(1, 0, 0), xreg = dataset$yts, :
NaNs produced
\end{verbatim}

@@

lmD: 0.001905 +/- 0.000317

lmY: 0.001905 +/- 0.000317

Arima: 0.001905 +/- 0.000497

@@

lmD: 0.001871 +/- 0.000311

lmY: 0.001871 +/- 0.000311

Arima: 0.001871 +/- 0.00048

@@

lmD: 0.002627 +/- 0.000234

lmY: 0.002627 +/- 0.000234

Arima: 0.002627 +/- 0.000357

@@

lmD: 0.002857 +/- 0.00023

lmY: 0.002857 +/- 0.00023

Arima: 0.002857 +/- 0.000337

@@

lmD: 1.027493 +/- 0.146835

lmY: 1.027517 +/- 0.146837

Arima: 1.088887 +/- 0.223551

@@

lmD: 0.821483 +/- 0.093059

lmY: 0.821496 +/- 0.093061

Arima: 0.821491 +/- 0.106018

@@

lmD: 0.231635 +/- 0.035413

lmY: 0.231639 +/- 0.035414

Arima: 0.231639 +/- 0.038541

@@

lmD: 0.185627 +/- 0.035397

lmY: 0.18563 +/- 0.035398

Arima: 0.185631 +/- 0.037388

@@

lmD: 0.484056 +/- 0.045622

lmY: 0.484065 +/- 0.045623

Arima: 0.484067 +/- 0.052795

@@

lmD: 0.004522 +/- 0.01809

lmY: 0.004522 +/- 0.018091

Arima: 0.004522 +/- 0.018546

@@

lmD: -0.01638 +/- 0.016701

lmY: -0.01638 +/- 0.016702

Arima: -0.01638 +/- 0.016967

@@

lmD: 0.513947 +/- 0.066925

lmY: 0.513956 +/- 0.066926

Arima: 0.513955 +/- 0.073889

@@

lmD: 0.62079 +/- 0.075699

lmY: 0.620801 +/- 0.075701

Arima: 0.620798 +/- 0.084973

@@

lmD: 1.376585 +/- 0.138013

lmY: 1.376613 +/- 0.138016

Arima: 1.376617 +/- 0.159843

@@

lmD: 0.00152 +/- 0.000147

lmY: 0.00152 +/- 0.000147

Arima: 0.00152 +/- 0.000172

@@

lmD: 0.00047 +/- 6.5e-05

lmY: 0.00047 +/- 6.5e-05

Arima: 0.00047 +/- 7.4e-05

@@

lmD: 0.000371 +/- 6.8e-05

lmY: 0.000371 +/- 6.8e-05

Arima: 0.000371 +/- 7.5e-05

@@

lmD: 2.4e-05 +/- 3.2e-05

lmY: 2.4e-05 +/- 3.2e-05

Arima: 2.4e-05 +/- 3.6e-05

@@

lmD: -9e-06 +/- 2.8e-05

lmY: -9e-06 +/- 2.8e-05

Arima: -9e-06 +/- 3.3e-05

@@

lmD: 0.001043 +/- 0.000117

lmY: 0.001043 +/- 0.000117

Arima: 0.001043 +/- 0.000134

@@

lmD: 0.00124 +/- 0.000128

lmY: 0.00124 +/- 0.000128

Arima: 0.00124 +/- 0.000149

@@

lmD: 0.040357 +/- 0.004191

lmY: 0.040358 +/- 0.004191

Arima: 0.040358 +/- 0.004746

@@

lmD: 0.194018 +/- 0.214287

lmY: 0.194046 +/- 0.21429

Arima: 0.186379 +/- 0.278973

@@

lmD: 0.05596 +/- 0.153614

lmY: 0.055976 +/- 0.153616

Arima: 0.03062 +/- 0.246509

@@

lmD: 0.096383 +/- 0.153736

lmY: 0.096398 +/- 0.153738

Arima: 0.071517 +/- 0.241036

@@

lmD: -0.06688 +/- 0.139832

lmY: -0.066875 +/- 0.139835

Arima: -0.104892 +/- 0.240811

@@

lmD: -0.088196 +/- 0.139661

lmY: -0.088192 +/- 0.139663

Arima: -0.125787 +/- 0.23978

@@

lmD: 0.176855 +/- 0.193744

lmY: 0.176884 +/- 0.193747

Arima: 0.166242 +/- 0.263579

@@

lmD: 0.185582 +/- 0.202704

lmY: 0.18561 +/- 0.202708

Arima: 0.17647 +/- 0.269872

@@

lmD: 0.354016 +/- 0.243235

lmY: 0.35404 +/- 0.243239

Arima: 0.354135 +/- 0.247045

@@

lmD: 0.000568 +/- 0.000406

lmY: 0.000568 +/- 0.000406

Arima: 0.000566 +/- 0.000539

@@

lmD: 0.000409 +/- 0.00035

lmY: 0.000409 +/- 0.00035

Arima: 4e-04 +/- 0.000503

@@

lmD: 0.000433 +/- 0.000359

lmY: 0.000433 +/- 0.000359

Arima: 0.000424 +/- 0.000507

@@

lmD: 0.000213 +/- 0.000334

lmY: 0.000213 +/- 0.000334

Arima: 0.000198 +/- 0.000495

@@

lmD: 2e-04 +/- 0.000333

lmY: 2e-04 +/- 0.000333

Arima: 0.000184 +/- 0.000494

@@

lmD: 0.000567 +/- 0.000389

lmY: 0.000567 +/- 0.000389

Arima: 0.000564 +/- 0.000526

@@

lmD: 0.000568 +/- 0.000396

lmY: 0.000568 +/- 0.000397

Arima: 0.000565 +/- 0.000532

@@

lmD: 0.008854 +/- 0.005655

lmY: 0.008855 +/- 0.005655

Arima: 0.008895 +/- 0.005992

@@

Arima: 0.231639 +/- 0.038541

@@

\begin{verbatim}
Warning: Removed 15 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 36 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 3 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 36 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 4 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 36 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 3 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 36 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 3 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

lmY: 346.8852 +/- 33.74613

@@

lmY: 133.6263 +/- 11.25784

@@

lmY: 0.232888 +/- 0.050234

@@

lmY: 0.202917 +/- 0.037683

@@

\begin{verbatim}
2024-04-13 09:28:09.9 athan@tyler GHI_enh_04_investigate.R 3.383829 mins
\end{verbatim}
